\begin{comment}
Guidelines:
Seiten: 50
Präsentation: 30 min / Disskusion: 15 min
sonarqube als code scan (nur ein vorschlag)
\end{comment}

\import{content/}{einleitung}
\import{content/}{anwendungsfeld}

\import{content/}{grundlagen}
\import{content/}{problem}

\section{Vobereiten und verwandte Arbeiten}
%vielleicht brauche ich diese sektion gar nicht ?

\subsection{Load Balancer}
%was für load balancer gibt es? was haben diese für eigenschaften?

\subsection{Shared Subscriptions}

\begin{comment}
diese lösen das problem der teuren clients ABER clients müssen dann möglichst optimal auf die broker verteilt werden
-> load balancer

iot mqtt threat model ? maybe show this ?

- If your work is based on preliminary work, then outline this preliminary work: "The de-ployment into production is itself semi-automatic. In a continuous integration pipeline..."
- Do some research forrelated work, e.g., commercial products, research prototypes or con-ceptual research that have the same or similar objectives like your work. Compare and de-lineate your work with/from the related work.
- Keep an eye on the proper citation of the works you are describing
- Conclude this chapter with some insufficiencies or shortcomings of the preliminary or related work. This should motivate the necessity of your work.
\end{comment}

\import{content/}{solution}
\import{content/}{implementation}

% TODO die beiden kapitel brauche ich glaube nicht
%\section{Erprobung}
%\subsection{Lastverteilung}
%If possible, do an (external) evaluation of your work. If you have developed some kind of tool, let us-ers test it, gather their feedback and describe that here. (Negative feedback will not contribute to a downgrading).
%\section{Zeitplanung und Arbeitspakete}

\begin{comment}
- In the initiation phase, we agree on work packages. Give a (tabular overview) of which work packages have been finalized
  - to what degree
  - and in which time frame
- Please described the unforeseen difficulties that resulted in unfinished or abandoned work packages
\end{comment}

\section{Ausblick}

\newpage
\begin{comment}
- Again, summarize your work. This time you can assume that reader have read the rest of the document, i.e., you are free to use even domain-specific terms.
- In case of a master thesis in "Technische Informatik", you will have to provide an addi-tional "technical report" in English of 4-8 pages (cf. examination regulation document, §28, 1d). It is okay for me if you use this technical report as the summary here.
- Usually, during your project or thesis new and extended questions arise that are not dealt with in your project or thesis due effort reasons. Please delineate these in the outlook.
\end{comment}
